All Samples Model

### 2018-03-23 AllSamplesModel.Rmd
updating shiny app

globalCN.plot = globalCN.plot + theme(legend.position = 'none') + labs(y='mean adj. seg.', title='All samples')
ggsave(filename='plots/globalCN.png', plot=globalCN.plot + labs(title=''), width=16, height=4.6, units='in', dpi=300)
globalCN.plot

## NDBE
nb.status <- c('Progressor'=paste('Progressor (n=',length(unique(subset(globalCNdf, Status == 'Progressor' & Pathology == 'BE')$variable)), ')', sep=''),
              'Non-Progressor'=paste('Non-Progressor (n=',length(unique(subset(globalCNdf, Status == 'Non-Progressor' & Pathology == 'BE')$variable)),')', sep=''))
globalBECN.plot = cn.mtn.plot(subset(globalCNdf, seg.type != 'arms' & Pathology == 'BE'), labeller(Status=nb.status, chr=label_value)) + labs(title='NDBE samples only')
globalBECN.plot = globalBECN.plot + theme(legend.position = 'none') + labs(y='mean adj.seg.', title="Non-Dysplastic Barrett's Samples") 
ggsave(filename='plots/globalBECN.png', plot=globalBECN.plot + labs(title=''), width=16, height=4.6, units='in', dpi=300)
globalBECN.plot

@@

```{r model, message=F, warning=F, echo=F, fig.height=16, fig.width=16}
#folds = 10; splits = 5 
# file = paste(cache.dir, 'all.pt.alpha.Rdata', sep='/')
# if (file.exists(file)) {
#   message(paste("loading", file))
#   load(file, verbose=T)
# } else {
#   stop(paste("No model file", file, "found"))
# }

@@

@@

```{r, echo=F, warning=F, message=F, fig.height=10, fig.width=20}
min.theme = theme(text=element_text(size=12), panel.background=element_blank(), strip.background=element_rect(fill="grey97"), strip.text.y = element_text(size=6),
                   strip.text.x = element_text(size=12), axis.text = element_blank(), axis.ticks = element_blank(),
                   axis.line=element_line(color='black'), panel.grid.major.y =element_line(color='grey95'), panel.grid.major.x = element_blank(),
                   panel.border = element_rect(color="grey", fill=NA, size=0.5), panel.spacing.x = unit(0, 'lines'), panel.spacing.y = unit(0.1, 'lines')   )

mtn.spatial<-function(df, b, limits, title='', pal=NULL) {
  if (is.null(pal))
    pal = RColorBrewer::brewer.pal(length(limits), 'Set2')

  df = merge(df, b[,c('Samplename','Endoscopy.Year','months.before.final','Block','ogj')], by.x='variable',by.y='Samplename')
  df$ogj = factor(df$ogj, ordered = T)
  df$ogj = factor(df$ogj, levels=rev(levels(df$ogj)), ordered = T)
  #pal = pal[which(limits %in% levels(df$nl))]

  altcolor = c(RColorBrewer::brewer.pal(9, 'Greys')[2],RColorBrewer::brewer.pal(9, 'Greys')[4])
  fills = c()
  for (yr in sort(unique(df$Endoscopy.Year))) {
    ac = (which(sort(unique(df$Endoscopy.Year)) == yr) %% 2) + 1
    fills = c(fills, rep(altcolor[ac], length(which(table(subset(df, Endoscopy.Year == yr)$ogj) > 0))))
  }

  blanklabel <- function(s) {
    return('')
  }

  p = ggplot(df, aes(x=chr.length)) + facet_grid(Endoscopy.Year+ogj~chr, scales='free', space='free_x', labeller = labeller(.multi_line = F)) +
      geom_rect(aes(xmin=start, xmax=end, ymin=0, ymax=mean.value, fill=ogj), show.legend=T) + 
      scale_fill_manual(values=pal, limits=limits,  name='OGJ Dist.') +
      labs(title=title, x='') + min.theme

  legend = get.legend(p)
  p = p + theme(legend.position = 'none')

  g = ggplot_gtable(ggplot_build(p))
  strips = grep('strip-r', g$layout$name)

  for (n in 1:length(strips)) {
    i = strips[n]
    j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
    g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[n]
  }

  #grid.arrange(g)
  return(list('grob'=g, 'legend'=legend))
  #grid::grid.draw(g)  
  #return(g)
}

back$ogj = back$nl
back$ogj[which(back$nl > 0 & back$nl < 3)] = 1 
back$ogj[which(back$nl > 3 & back$nl < 7)] = 2 
back$ogj[which(back$nl >= 7)] = 3

@@

p2 = mtn.spatial(subset(globalCNdf, Patient == 20 & seg.type != 'arms'), back, ogjLimits,'Patient 20 (P)' )
p6 = mtn.spatial(subset(globalCNdf, Patient == 51 & seg.type != 'arms'), back,ogjLimits,'Patient 51 (NP)' )

@@

```{r, echo=F, fig.width=2, fig.height=4}

ggsave(filename='plots/spatial/patient_20.png', plot=grid.arrange(p2$grob), width=14, height=6, units='in', dpi=300)
ggsave(filename='plots/spatial/patient_51.png', plot=grid.arrange(p6$grob), width=14, height=6, units='in', dpi=300)

@@

rp = ggplot(riskPath, aes(Pathology, ratio*100)) + 
  geom_bar(aes(group=Risk, fill=Risk),stat='identity', position=position_stack()) + 
  scale_fill_manual(values=riskCols, limits=levels(riskPath$Risk)) + 
  scale_color_manual(values=c('white','black','white'), limits=levels(pred.confidence$Risk) ) +
  geom_text(data=pathTotal, aes(label=paste('n=',nPath,sep=''), x=Pathology, y=102), position=position_stack()) +
  geom_text(data=subset(riskPath, ratio>0), aes(group=Risk,label=paste(ratio*100,'%',sep=''), color=Risk), position=position_stack(vjust = 0.5), show.legend = F) +
  facet_grid(~Status, scales='free_x', space = 'free_x') + plot.theme + 
  labs(title='Samples predicted by pathology', y='% Predicted', x='Pathology') + theme(legend.position = 'none')
rp

@@

p53Path$p53.Status = factor(p53Path$p53.Status, ordered = T)
p53Path = arrange(p53Path, Pathology, p53.Status)
col = brewer.pal(11, "PRGn")[c(10,2)]
rp = ggplot(p53Path, aes(Pathology, ratio*100, group=Pathology, fill=p53.Status)) + geom_bar(stat='identity', position = position_stack()) +
  scale_fill_manual(values=col, name='p53 IHC', labels=c('Normal','Aberrant')) + 
  geom_text(aes(label=paste('n=',nPath,sep=''), x=Pathology, y=103)) +
  geom_text(aes(label=paste(ratio*100,'%',sep='')), position=position_stack(vjust = 0.5), size=5,color='white') +
  plot.theme + labs(title='', y='% Predicted', x='Pathology') + theme(legend.position = 'bottom')
rp
ggsave(filename='plots/p53_pred.png', plot=rp, width=4.5, height=3.6, units='in', dpi=300, scale=1.2)

@@

rp = ggplot(endos.r, aes(x=brks, y=pred.r*100, ymin=(pred.r-`sem(P)`)*100, ymax=(pred.r+`sem(P)`)*100, group=brks)) + ylim(0,105) +
#  geom_bar(data=endos.m, aes(x=brks, y=pred.r*100, group=brks), stat='identity', fill=riskCols[2], show.legend = F, alpha=0.5) +
#  geom_text(data=endos.m, aes(y=round(pred.r*100+2), label=paste(round(pred.r*100), '%', sep='')), color='grey45') +
  geom_bar(stat='identity', fill=riskCols[3], show.legend = F) + 
  geom_errorbar(color='grey21', width=0.2) +
  geom_text(aes(y=3, label=paste(round(pred.r*100), '%', sep='')), color='white') +
  geom_text(aes(y=pred.r*100-8, label=paste('n=',n.endo,'\ns=',n.samp,sep='')), color='white') + 
  labs(x='Months prior to endpoint', y='Percent predicted', title='Predictions prior to final endoscopy', subtitle='n = #endoscopies, s = #samples') +
  plot.theme + theme( axis.text.x=element_text(angle=45,hjust=1) ) 
rp
ggsave(filename='plots/pred_endo.png', plot=rp, width=5.8, height=4.5, units='in', dpi=300, scale=1)

@@

```{r heatmaps, echo=F, warning=F, message=F, fig.width=5, fig.height=5 }
back$nl = factor(back$nl, ordered=T)
back$Risk = factor(back$Risk, levels=c('Low','Moderate','High'), ordered = T)
back$Patient = factor(as.numeric(back$Patient), ordered = T)

table(rev(arrange(subset(back, Patient == 19), brks)$brks))

#pred.tiles(subset(back, Patient %in% c(48)), ncol=1, cols=myPal, probs=T) + labs(title='') + theme(legend.position = 'none')
#pred.tiles(subset(back, Patient %in% c(33)), ncol=1, cols=myPal, probs=T) + labs(title='')+ theme(legend.position = 'none')
#pred.tiles(subset(back, Patient %in% c(89)), ncol=1, cols=myPal, probs=T) + labs(title='')+ theme(legend.position = 'none')
```

```{r, echo=F, warning=F, message=F, fig.width=5, fig.height=15 }
#back = back %>% group_by(Patient) %>% dplyr::mutate(endo.num = as.integer(droplevels(brks)) )
#back$endo.num = factor(back$endo.num, ordered = T)

#back$endo.num = factor(as.integer(back$brks))
#back = back %>% group_by(Patient) %>% dplyr::mutate(endo.num = ifelse(endo.num == max(endo.num), 'End', endo.num)   )

ga = grid.arrange(
  pred.tiles(subset(back, Patient %in% c(13,20,34,56,60,48) & Status == 'P'), ncol=1, cols=myPal, probs=T) + labs(title='Progressors') + theme(legend.position = 'none'),
  pred.tiles(subset(back, Patient %in% c(15,16,21,3,45,19) & Status == 'NP'), ncol=1, cols=myPal, probs=T) + labs(title='Non-Progressors') + theme(legend.position = 'none'),
  ncol=2)
ga

#ggsave('plots/ex_pt_heatmap.png', plot=ga, width=6, height=15, units='in', dpi=300)

@@

  p = pred.tiles(b, cols=riskCols, ylim=lim,  probs=F, scales='free', space='free') + labs(title='', x='', y='') + theme(legend.position = 'none', strip.text = element_blank(), plot.margin = unit(c(0,0.2,0,0), 'cm'))
  ggsave(paste('plots/heatmaps/P/pt_',i,'.png', sep=''), plot=p, height=get.h.scale(b), width=get.w.scale(b), unit='in', dpi=300 )
}
b = subset(back, Patient == 32)
lim = c(1:4)
p = pred.tiles(b, cols=riskCols, ylim=lim,  probs=F, scales='free', space='free') + labs(title='', x='', y='') + theme(legend.position = 'none', strip.text = element_blank(), plot.margin = unit(c(0,0.2,0,0), 'cm'))
  ggsave(paste('plots/heatmaps/P/pt_32.png', sep=''), plot=p, height=4, width=get.w.scale(b), unit='in', dpi=300 )

@@

  p = pred.tiles(b, cols=riskCols, ylim=lim,  probs=F, scales='free', space='free') + labs(title='', x='', y='') + theme(legend.position = 'none', strip.text = element_blank(), plot.margin = unit(c(0,0.2,0,0), 'cm'))
  ggsave(paste('plots/heatmaps/NP/pt_',i,'.png', sep=''), plot=p, height=get.h.scale(b,9), width=get.w.scale(b), unit='in', dpi=300 )
}

all = pred.tiles(back, cols=riskCols,  probs=F, scales='free', space='free') + labs(title='', x='', y='') + theme(legend.position = 'bottom')
riskLegend = get.legend(all)

@@

file = paste(cache.dir, 'model_data.Rdata', sep='/')
if (!file.exists(file))
  stop(paste("Missing data file", file))
load(file, verbose=T)
file = paste(cache.dir, 'all.pt.alpha.Rdata', sep='/')
if (!file.exists(file))
  stop(paste("Missing data file", file))
load(file, verbose=T)
rm(dysplasia.df,coefs,plots,labels)

@@

m = subset(m, Type != 'Normal blood')
m$Type = droplevels(m$Type)
pr = ggplot(m, aes(Type, RR, fill=Type)) + 
  geom_jitter(width=0.2, aes(color=RR)) + 
  scale_color_gradientn(colors = myPal,  name='') + 
  geom_boxplot(outlier.colour = NA) + 
  scale_fill_manual(values = riskCols,  name='') + 
  labs(x='', y='RR', title='Predicted Relative Risk') + 
  theme(legend.position = 'none') + plot.theme 
pr

@@

p = p + theme(legend.position = 'none')
ggsave('plots/vignette/vig_34.png', plot=p, width=6, height=3.9,dpi=300)

@@

p = vig.plot(subset(back, Patient == 20), subset(patient.info, Patient == 20),cols=riskCols) + theme(legend.position = 'none')
ggsave('plots/vignette/vig_20.png', plot=p, width=6, height=3.9,dpi=300)

@@

## NP
p = vig.plot(subset(back, Patient == 3), subset(patient.info, Patient == 3),cols=riskCols) + theme(legend.position = 'none')
ggsave('plots/vignette/vig_3.png', plot=p, width=6, height=3.9,dpi=300)

@@

p = vig.plot(subset(back, Patient == 68), subset(patient.info, Patient == 68),cols=riskCols) + theme(legend.position = 'none')
ggsave('plots/vignette/vig_68.png', plot=p, width=6, height=3.9,dpi=300)

@@

```{r echo=F}
file = paste(cache.dir, 'all.pt.alpha.Rdata', sep='/')
load(file, verbose=T)
rm(plots, coefs, cv.patient)

@@

@@

>>>>

globalCN.plot = globalCN.plot + theme(legend.position = 'none') + labs(y='mean adj. seg.', title='All samples')

ggsave(filename='plots/globalCN.png', plot=globalCN.plot + theme(strip.text.y=element_blank(), strip.text.x=element_text(size=9), axis.text=element_blank()) + labs(x='', y='',title=''), width=8.3, height=2.4, units='in', dpi=300)

## NDBE
nb.status <- c('Progressor'=paste('Progressor (n=',length(unique(subset(globalCNdf, Status == 'Progressor' & Pathology == 'BE')$variable)), ')', sep=''),
              'Non-Progressor'=paste('Non-Progressor (n=',length(unique(subset(globalCNdf, Status == 'Non-Progressor' & Pathology == 'BE')$variable)),')', sep=''))
globalBECN.plot = cn.mtn.plot(subset(globalCNdf, seg.type != 'arms' & Pathology == 'BE'), labeller(Status=nb.status, chr=label_value)) + labs(title='NDBE samples only')
globalBECN.plot = globalBECN.plot + theme(legend.position = 'none') + labs(y='mean adj.seg.', title="Non-Dysplastic Barrett's Samples")

ggsave(filename='plots/globalBECN.png', plot=globalBECN.plot + theme(strip.text.y=element_blank(), strip.text.x=element_text(size=9), axis.text=element_blank()) + labs(x='', y='',title=''), width=8.3, height=2.4, units='in', dpi=300)
globalBECN.plot

@@

```{r model, message=F, warning=F, echo=F, fig.height=16, fig.width=16}
file = paste(cache.dir, 'all.pt.alpha.Rdata', sep='/')
if (file.exists(file)) {
  message(paste("loading", file))
  load(file, verbose=T)
} else {
  stop(paste("No model file", file, "found"))
}

@@

chtable = ch[,c('hazards','coef','stability','label')]
chtable = chtable[,c('label','hazards', 'coef')]
chtable$coef[which(chtable$coef > 0)] = 'Gain'
chtable$coef[which(chtable$coef != 'Gain')] = 'Loss'
colnames(chtable) = c('Location','Hazard', 'Gain/Loss')
chtable$Hazard = round(chtable$Hazard, 3)
write.table(chtable, sep='\t', quote=F, row.names = F, file='hazards.txt')

@@

```{r, echo=F, warning=F, message=F, fig.height=10, fig.width=20}
back$ogj = back$nl
back$ogj[which(back$nl > 0 & back$nl < 3)] = 1 
back$ogj[which(back$nl > 3 & back$nl < 7)] = 2 
back$ogj[which(back$nl >= 7)] = 3

@@

p2 = mtn.spatial(subset(globalCNdf, Patient == 20 & seg.type != 'arms'), back, ogjLimits,'' )
grid.arrange(p2$grob)

p6 = mtn.spatial(subset(globalCNdf, Patient == 51 & seg.type != 'arms'), back,ogjLimits,'' )

ggsave(filename='plots/spatial/patient_20.png', plot=grid.arrange(p2$grob), width=7.2, height=3, units='in', dpi=300)
ggsave(filename='plots/spatial/patient_51.png', plot=grid.arrange(p6$grob), width=7.2, height=3, units='in', dpi=300)

@@

@@

#riskPath$Pathology = as.character(riskPath$Pathology)
#riskPath$Pathology[riskPath$Pathology == 'BE'] = 'NDBE'
#riskPath$Pathology = factor(riskPath$Pathology, levels=c('NDBE','ID','LGD','HGD','IMC'), ordered=T)
rp = ggplot(riskPath, aes(Pathology, ratio*100)) + 
  geom_bar(aes(group=Risk, fill=Risk),stat='identity', position=position_stack()) + 
  scale_fill_manual(values=riskCols, limits=levels(riskPath$Risk)) + 
  scale_color_manual(values=c('black','black','black'), limits=levels(pred.confidence$Risk) ) +
  scale_x_discrete(labels=c('NDBE','ID','LGD','HGD','IMC')) +
  geom_text(data=pathTotal, aes(label=paste('n=',nPath,sep=''), x=Pathology, y=102), position=position_stack()) +
  geom_text(data=subset(riskPath, ratio>0), aes(group=Risk,label=paste(ratio*100,'%',sep=''), color=Risk), position=position_stack(vjust = 0.5), show.legend = F) +
  facet_grid(~Status, scales='free_x', space = 'free_x') + plot.theme + 
  labs(title='Samples predicted by pathology', y='% Predicted', x='Pathology') + theme(legend.position = 'none')
rp

@@

p53Path$p53.Status = factor(p53Path$p53.Status, ordered = T)
p53Path = arrange(p53Path, Pathology, p53.Status)
col = brewer.pal(11, "PRGn")[c(10,2)]
rp = ggplot(p53Path, aes(Pathology, ratio*100, group=Pathology, fill=p53.Status)) + geom_bar(stat='identity', position = position_stack()) +
  scale_fill_manual(values=col, name='p53 IHC', labels=c('Normal','Aberrant')) + 
  scale_x_discrete(labels=c('NDBE','ID','LGD','HGD','IMC')) +
  geom_text(aes(label=paste('n=',nPath,sep=''), x=Pathology, y=103)) +
  geom_text(aes(label=paste(ratio*100,'%',sep='')), position=position_stack(vjust = 0.5), size=5,color='white') +
  plot.theme + labs(title='', y='% Predicted', x='Pathology') + theme(legend.position = 'bottom')
rp
ggsave(filename='plots/p53_pred.png', plot=rp, width=4.5, height=3.6, units='in', dpi=300, scale=1.2)

@@

rp = ggplot(endos.r, aes(x=brks, y=pred.r*100, ymin=(pred.r-`sem(P)`)*100, ymax=(pred.r+`sem(P)`)*100, group=brks)) + ylim(0,105) +
#  geom_bar(data=endos.m, aes(x=brks, y=pred.r*100, group=brks), stat='identity', fill=riskCols[2], show.legend = F, alpha=0.5) +
#  geom_text(data=endos.m, aes(y=round(pred.r*100+2), label=paste(round(pred.r*100), '%', sep='')), color='grey45') +
  geom_bar(stat='identity', fill=riskCols[3], show.legend = F) + 
  geom_errorbar(color='grey21', width=0.2, alpha=0.5) +
  geom_text(aes(y=pred.r*100+2, label=paste(round(pred.r*100), '%', sep='')), color='black') +
  geom_text(aes(y=10, label=paste('n=',n.endo,'\ns=',n.samp,sep='')), color='white') + 
  labs(x='Months prior to endpoint', y='Percent predicted', title='Predictions prior to final endoscopy', subtitle='n = #endoscopies, s = #samples') +
  plot.theme + theme( axis.text.x=element_text(angle=45,hjust=1) ) 
rp
ggsave(filename='plots/pred_endo.png', plot=rp, width=5.8, height=4.5, units='in', dpi=300, scale=1)

@@

```{r heatmaps, echo=F, warning=F, message=F}
back$nl = factor(back$nl, ordered=T)
back$Risk = factor(back$Risk, levels=c('Low','Moderate','High'), ordered = T)
back$Patient = factor(as.numeric(back$Patient), ordered = T)

@@

back$months.before.final = round(back$months.before.final)

for (i in unique(subset(back, Status == 'P')$Patient)) {
  b = subset(back, Patient == i)
  if (i == 89) b[which(b$Pathology == 'HGD'),'months.before.final'] = 0

  lim = c(1:7)
  if (b$max.block[1] < 6) lim = c(1:5)
  if (b$max.block[1] > 2 & b$max.block[1] < 4) lim = c(1:3)
  if (b$max.block[1] <= 2) lim = c(1:2)

  p = pred.tiles(b, cols=riskCols, ylim=lim,  probs=F, path=F, scales='free', space='free') + labs(title='', x='', y='') + theme(legend.position = 'none', strip.text = element_blank(), plot.margin = unit(c(0,0.2,0,0), 'cm'))
  ggsave(paste('plots/heatmaps/P_nopath/pt_',i,'.png', sep=''), plot=p, height=get.h.scale(b), width=get.w.scale(b), unit='in', dpi=300 )

    p = pred.tiles(b, cols=riskCols, ylim=lim,  probs=F, path=6, scales='free', space='free') + labs(title=i,x='months', y='location') + theme(legend.position = 'none', strip.text = element_blank(), axis.text = element_text(size=9), plot.margin = unit(c(0,0.2,0,0), 'cm'))
  ggsave(paste('plots/heatmaps/P/pt_',i,'.png', sep=''), plot=p, height=get.h.scale(b), width=get.w.scale(b), unit='in', dpi=300 )
}

b = subset(back, Patient == 32)
lim = c(1:4)
p = pred.tiles(b, cols=riskCols, ylim=lim,  probs=F, scales='free', space='free') + labs(title='', x='', y='') + theme(legend.position = 'none', strip.text = element_blank(), plot.margin = unit(c(0,0.2,0,0), 'cm'))
  ggsave(paste('plots/heatmaps/P_nopath/pt_32.png', sep=''), plot=p, height=4, width=get.w.scale(b), unit='in', dpi=300 )

p = pred.tiles(b, cols=riskCols, ylim=lim,  probs=F, path=6, scales='free', space='free') + labs(title='32', x='months',y='location') + theme(legend.position = 'none', strip.text = element_blank(), axis.text = element_text(size=9), plot.margin = unit(c(0,0.2,0,0), 'cm'))
  ggsave('plots/heatmaps/P/pt_32.png', plot=p, height=4, width=get.w.scale(b), unit='in', dpi=300 )

@@

for (i in unique(subset(back, Status == 'NP')$Patient)) {
  b = subset(back, Patient == i)
  lim = c(1:9)
  if (b$max.block[1] < 6) lim = c(1:5)
  if (b$max.block[1] < 4) lim = c(1:3)
  if (b$max.block[1] < 3) lim = c(1:2)

  p = pred.tiles(b, cols=riskCols, ylim=lim,  probs=F, scales='free', space='free') + labs(title='', x='', y='') + theme(legend.position = 'none', strip.text = element_blank(), plot.margin = unit(c(0,0.2,0,0), 'cm'))
  ggsave(paste('plots/heatmaps/NP_nopath/pt_',i,'.png', sep=''), plot=p, height=get.h.scale(b,9), width=get.w.scale(b), unit='in', dpi=300 )

  p = pred.tiles(b, cols=riskCols, ylim=lim,  probs=F, path=6, scales='free', space='free') + labs(title=i,x='months',y='location') + theme(legend.position = 'none', strip.text = element_blank(), axis.text = element_text(size=9), plot.margin = unit(c(0,0.2,0,0), 'cm'))
  ggsave(paste('plots/heatmaps/NP/pt_',i,'.png', sep=''), plot=p, height=get.h.scale(b), width=get.w.scale(b), unit='in', dpi=300 )
}

all = pred.tiles(back, cols=riskCols, path=4, probs=F, scales='free', space='free') + labs(title='', x='', y='') + theme(legend.position = 'bottom')
riskLegend = get.legend(all)

@@

file = paste(cache.dir, 'model_data.Rdata', sep='/')
if (!file.exists(file))
  stop(paste("Missing data file", file))
load(file, verbose=T)
file = paste(cache.dir, 'all.pt.alpha.Rdata', sep='/')
if (!file.exists(file))
  stop(paste("Missing data file", file))
load(file, verbose=T)
rm(coefs,plots,labels)

@@

m = subset(dspred, Type != 'Normal blood')
m$Type = droplevels(m$Type)
pr = ggplot(m, aes(Type, RR, fill=Type)) + 
  geom_jitter(width=0.2, aes(color=RR)) + 
  scale_color_gradientn(colors = myPal,  name='') + 
  geom_boxplot(outlier.colour = NA) + 
  scale_fill_manual(values = riskCols,  name='') + 
  labs(x='', y='RR', title='Predicted Relative Risk') + 
  theme(legend.position = 'none') + plot.theme 
pr

@@

p = p + theme(legend.position = 'none')
ggsave('plots/vignette/vig_34.png', plot=p + coord_flip() + labs(y='', x=''),width=4.6, height=4.2,dpi=300)
#ggsave('plots/vignette/vig_34.png', plot=p, width=6, height=3.9,dpi=300)

@@

p = vig.plot(subset(back, Patient == 20), subset(patient.info, Patient == 20),cols=riskCols) + theme(legend.position = 'none')
ggsave('plots/vignette/vig_20.png', plot=p + coord_flip() + labs(y='', x=''), width=4.6, height=4.2,dpi=300)
#ggsave('plots/vignette/vig_20.png', plot=p, width=6, height=3.9,dpi=300)

@@

## NP
p = vig.plot(subset(back, Patient == 3), subset(patient.info, Patient == 3),cols=riskCols) + theme(legend.position = 'none')
ggsave('plots/vignette/vig_3.png', plot=p + coord_flip() + labs(y='', x=''),width=4.6, height=4.2,dpi=300)
#ggsave('plots/vignette/vig_3.png', plot=p, width=6, height=3.9,dpi=300)

@@

p = vig.plot(subset(back, Patient == 68), subset(patient.info, Patient == 68),cols=riskCols) + theme(legend.position = 'none')
ggsave('plots/vignette/vig_68.png', plot=p + coord_flip() + labs(y='', x=''), ,width=4.6, height=4.2,dpi=300)
#ggsave('plots/vignette/vig_68.png', plot=p, width=6, height=3.9,dpi=300)

@@

```{r echo=F}
file = paste(cache.dir, 'all.pt.alpha.Rdata', sep='/')
load(file, verbose=T)
rm(plots, coefs, cvs)

@@

dspred = dspred %>% dplyr::mutate( 'Adj. Prob'=1/(1+exp(-RR+abs(offsetMean)) ))

ggplot(dspred, aes(Type, `Adj. Prob`)) + geom_jitter()

@@

m = melt(dspred, measure.vars=c('Prob','Adj. Prob'))
colors = myPal[seq(2, length(myPal), round(length(myPal)/4))]
pr = ggplot(m, aes(variable, value, fill=Type)) + facet_grid(~Type, scales='fixed') + 
  geom_jitter(width=0.2, aes(color=value)) + 
  scale_color_gradientn(colors = myPal,  name='') + 
  geom_boxplot(outlier.colour = NA) + 
  scale_fill_manual(values = colors,  name='') + 
  labs(x='', y='Relaive Risk', title='Comparing Relative Risk') + 
  theme(legend.position = 'none', axis.text.x = element_text(angle=45,hjust=1)) + plot.theme 
pr
